Automated Program Verification and Synthesis of Embedded \& Cyber-physical Systems: Advances and Challenges

### 2017-08-03 paper.tex
reviewed section 7
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>
reviewed section 5
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

This position paper tackles seven major problems in computer-aided verification and synthesis for embedded systems, which are (partially) open in current published research.

\textbf{(RP1)} provision of suitable encoding into SMT \cite{BarrettSST09}, which may extend background theories typically supported by SMT solvers, with the goal of reasoning accurately and effectively about realistic embedded programs.

@@

\textbf{(RP3)} proof of correctness and timeliness of embedded systems, by taking into account stringent constraints imposed by hardware platforms.

@@

\textbf{(RP7)} provision of a unified framework, which is able to tackle high and low level properties, as well as system behavior, with the potential to lead to another degree of completeness, in such a way that every implementation aspect of an embedded system is addressed and evaluated.

@@

ML techniques are already being used in the software verification area \cite{mlswverif,nguyen,bridge,babic07}. For instance, Hamel~\cite{mlswverif} proposed to induce a theory, through ML, that fits a test set for a program, in such a way that it implements the respective test set. Phuc \cite{nguyen}, in turn, applied decision tree C4.5 and multilayer perceptron to annotated programs (metrics related to structure and semantics) and tackled the generation of test sets satisfying the desired constraints. Finally, Bridge studied the automation of heuristic selection based on features, regarding first-order logic theorem proving, and Hutter {\it et. al} \cite{babic07} showed that ML can be used for improving SAT solvers regarding huge verification tasks, when applied to parameter tuning~\cite{babic07}. Given what was presented, it seems worthwhile to pursue the integration of ML to BMC-based checkers, specifically ESBMC, mainly regarding solver tuning. In addition, ML can also be used for invariant computation and strengthening, which is a major bottleneck in \textit{k}-induction verification based on invariant algorithms.

>>>>

This position paper tackles seven major problems in computer-aided verification and synthesis for ECPS, which are (partially) open in current published research.

\textbf{(RP1)} provision of suitable encoding into SMT \cite{BarrettSST09}, which may extend background theories typically supported by SMT solvers, with the goal of reasoning accurately and effectively about realistic ECPS.

@@

\textbf{(RP3)} proof of correctness and timeliness of ECPS, by taking into account stringent constraints imposed by hardware platforms.

@@

\textbf{(RP7)} provision of a unified framework, which is able to tackle high and low level properties, as well as system behavior, with the potential to lead to another degree of completeness, in such a way that every implementation aspect of ECPS is addressed and evaluated.

@@

ML techniques are already being used in the software verification area \cite{mlswverif,nguyen,bridge,babic07}. For instance, Hamel~\cite{mlswverif} proposed to induce a theory, through ML, that fits a test set for a program, in such a way that it implements the respective test set. Phuc \cite{nguyen}, in turn, applied decision tree C4.5 and multilayer perceptron to annotated programs (metrics related to structure and semantics) and tackled the generation of test sets satisfying the desired constraints. Finally, Bridge studied the automation of heuristic selection based on features, regarding first-order logic theorem proving, and Hutter {\it et. al} \cite{babic07} showed that ML can be used for improving SAT solvers regarding huge verification tasks, when applied to parameter tuning~\cite{babic07}. Given what was presented, it seems worthwhile to pursue the integration of ML to BMC-based checkers, mainly regarding solver tuning. In addition, ML can also be used for invariant computation and strengthening, which is a major bottleneck in \textit{k}-induction verification based on invariant algorithms.
